---
title: "Lab 00 - Hello IDS!"
author: "Luyanda"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Luyanda", "Abdullah", "Aaron", 
           "Chinedu", "Tommy"),
  github_username = c("LuyandaMadliwa", "AbdullahS_06 ", "aaronj2405", 
                      "chinedua26","tommys2626550"), 
  colour = c("red", "red", "red",
             "blue", "purple"),
  hobby = c("music", "running", "football", 
            "music", "running"),
  favourite_number = c(6, 7, 5, 8, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The resulting bar plot provides the favourite numbers of different team members, with their usernames on the x-axis, and the bar colours corresponding to the favourite colours of the relevant team member

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Usernames", 
          y = "Favourite Numbers",
          title = "Favourite Numbers vs. Usernames")
```

The labs function allows for the editing of the axis labels as well as the heading of a barplot produced by the ggplot function

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Alternate, more efficient methods of conveying the hobbies of the entire class visually
1. A word cloud, where the size of a given word denotes its popularity
2. If the total number of hobbies is sufficiently low, one could make use of a pie chart 
